### 2018-03-23 Paper/jaccardbaetica.tex
add new changes introduction

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. They allows us to highlight a part of mechanism of production and distribution of goods between different communities \citep{bevan_mediterranean_2014}.

%Roman trade has been an object of study in the last centuries.

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello
This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production centres. An ecology approach has been used to analyse the dispersion of stamps between amphora workshops.

@@

% Debate
The discussion about the production processes in Baetican area due to the lack of written sources
In archaeology, this debate has been widely studied in the last centuries (CITAR). Despite this knowledge the application of new methodology to understand the Roman trade has allowed us to deal with the complexity of Roman Market combined with archaeological evidence \citep{orengo_seeds_2016,brughmans_roman_2016,coto-sarmiento_maria_bayesian_????}. Specifically, our work pretend to detect economic processes in a microescala focused in a commercial product from a specific province \citep{isaksen_network_2006}.

@@

The production and distribution of olive oil in this ancient province were growing exponentially during almost three centuries \citep{remesal_concierto}. As a result, hundred of amphora workshops were created to support this high demand. These workshops were located along the river Guadalquivir and its tributary Genil supplying from the riverine connectivity to the Mediterranean and Atlantic \citep{garcia_vargas_enrique_formal_2010}.

>>>>

%primer párrafo más general---- especifico (¿dónde se ha aplicado?)
Material culture is one of the most frequent indicator of trade in the archaeological record. They allow us to highlight a part of mechanism of production and distribution of goods between different communities \citep{bevan_mediterranean_2014}.

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello
This paper aims to understand the production dynamics in relation to a specific area within Roman Empire. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production centres. An ecology approach has been used to analyse the dispersion of stamps between amphora workshops.

@@

% Debate
The discussion about the production processes in Baetican area due to the lack of written sources
In archaeology, this debate has been widely studied in the last centuries (CITAR). Despite this knowledge the application of new methodology to understand the Roman trade has allowed us to deal with the complexity of Roman Market combined with the archaeological evidence \citep{orengo_seeds_2016,brughmans_roman_2016,coto-sarmiento_maria_bayesian_????}. Specifically, our work pretend to detect economic processes in a microescala focused in a commercial product from a specific province \citep{isaksen_network_2006}.

@@

The production and distribution of olive oil in this ancient province were growing exponentially during almost three centuries \citep{remesal_concierto}. As a result, hundred of amphora workshops were created to support the high demand of Roman Empire. These workshops were located along the river Guadalquivir and its tributary Genil supplying from the riverine connectivity to the Mediterranean and Atlantic \citep{garcia_vargas_enrique_formal_2010}.
